Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}

### 2022-11-05 nakayama/paper.tex
Minor edits to formalization section

The next structure defined was a module over a commutative ring, the commutative-algebraic generalization of the notion of a vector
spaces over a fields,.  Here we needed to capture the notion of linear combinations of
coefficients and module vectors. This was done by dependently typed vectors,
i.e. lists parameterized by their length. Because there is an overload of the
term ``vector'', we will use that term to refer to module vectors, and use the
term ``list'' to mean length parameterized lists. As we don't use the simpler
kind of lists, this avoids any name collisions. A finitely generated module is
like the vector space \(\mathbf{R}^{n}\) in that there are finitely many
vectors which can generate all other vectors, for \(\mathbf{R}^{n}\) one such
collection of generators are \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 &
  \cdots & 0\end{pmatrix}^{T}\), \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 &
  \cdots & 0\end{pmatrix}^{T}\), \textellipsis, \(\mathbf{e}_{n} =
  \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\). In our code,
\texttt{M} is the type of module elements, \texttt{R} is the type of ring
elements which act as coefficients, and \texttt{t A n} is a list whose elements
are of type \texttt{A} and whose length is \texttt{n}.
% \begin{verbatim}
\begin{minted}{coq}
  Definition finitely_generated {n: nat}(basis: t M n) :=
    forall (vector: M),
      exists (coeffs: t R n),
        vector =M= linear_combin coeffs basis.
\end{minted}
% \end{verbatim}

>>>>

The next structure defined was a module over a commutative ring, the commutative-algebraic generalization of the notion of a vector
space over a field.

Toward proving 
Here we needed to formalize the notion of linear combinations of
coefficients and module vectors. This was done by dependently typed vectors,
i.e. lists parameterized by their length. Because there is an overload of the
term ``vector'', we will use that term to refer to module vectors, and use the
term ``list'' to mean length-parameterized lists. As we don't use the simpler
kind of lists, this avoids any name collisions. A finitely generated module is
like the vector space \(\mathbf{R}^{n}\) in that there are finitely many
vectors which can generate all other vectors, for \(\mathbf{R}^{n}\) one such
collection of generators are \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 &
  \cdots & 0\end{pmatrix}^{T}\), \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 &
  \cdots & 0\end{pmatrix}^{T}\), \textellipsis, \(\mathbf{e}_{n} =
  \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\). In our code,
\texttt{M} is the type of module elements, \texttt{R} is the type of ring
elements which act as coefficients, and \texttt{t A n} is a list whose elements
are of type \texttt{A} and whose length is \texttt{n}.
% \begin{verbatim}
\begin{minted}{coq}
  Definition finitely_generated {n: nat}(basis: t M n) :=
    forall (vector: M),
      exists (coeffs: t R n),
        vector =M= linear_combin coeffs basis.
\end{minted}
% \end{verbatim}
